Manuscript draft

### 2019-08-28 manuscript/manuscript draft.Rmd
updated manuscript draft

By including multiple fluxes in our analysis, we are able to explore the relationships between fluxes and their responses to climate. We find that fluxes are broadly consistent in their responses to climate drivers, suggesting that the importance of climate drivers on productivity is relatively invariant across fluxes. In addition, we show that carbon allocation between subsidiary fluxes does not vary significantly across broad climatic gradients. There is evidence that allocation between carbon fluxes does vary with factors such as stand age [@litton_carbon_2007], nutrient availability [@litton_carbon_2007; @gill-belowground_2016], forest structure [@taylor_greater_2019], elevation [@moser_elevation_2011], and water availability [@newman_above-_2006]. That we do not see consistent patterns of variation in allocation across climatic gradients indicates that the pressures influencing shifts in allocation between fluxes occur on local scales, and that shifts in allocation occur as a response to fluctuations in local environmental conditions.

>>>>

By including multiple fluxes in our analysis, we are able to explore the relationships between fluxes and their responses to climate. We find that fluxes are broadly consistent in their responses to climate drivers, suggesting that the importance of climate drivers on productivity is relatively invariant across fluxes. In addition, we show that carbon allocation between subsidiary fluxes does not vary significantly across broad climatic gradients. There is evidence that allocation between carbon fluxes does vary with factors such as stand age [@litton_carbon_2007], nutrient availability [@litton_carbon_2007; @gill_belowground_2016], forest structure [@taylor_greater_2019], elevation [@moser_elevation_2011], and water availability [@newman_above-_2006]. That we do not see consistent patterns of variation in allocation across climatic gradients indicates that the pressures influencing shifts in allocation between fluxes occur on local scales, and that shifts in allocation occur as a response to fluctuations in local environmental conditions.
